Preliminary Draft

### 2021-07-26 article/draft.tex
small changes after discussion with Shaden

In this article we have reviewed three broad categories of mainstream platforms' interventions to tackle misinformation: suspension of accounts, introduction of notices and flags and reducing the visibility of content. For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article. We have provided a methodology that can be useful for third-party monitoring, which aims to investigate platforms' interventions regarding content.  All the code needed to collect the data, create the figures and reproduce the study can be found on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}. Hence the academic community can easily implement and reproduce our methodology for the purposes of bringing to the society insights concerning the debate around misinformation. In the light of the present research, we discuss in this section data and policy related recommandations.

\subsection{Data related recommendations}

@@

{\bf Lack of data.} First, when Facebook, Twitter or YouTube intervene by suspending an account, a page or a channel, the data disappears. It can no longer be accessed via scrapping or via the available APIs for the purposes of scientific research. This hampers the investigation of how platforms moderate content. To further illustrate this point, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$. We selected $94$ Facebook pages corresponding to our criteria. We then tried to collect the posts on these pages in January $2021$. But we discovered that $11$ pages could no longer be found and that the related data had disappeared from the CrowdTangle API. Similarly, when a YouTube channel gets suspended or a YouTube video is deleted the data related to them is removed from the YouTube API. For instance, the original list of YouTube videos from table \ref{tab2} with failed fact-checks, had over $200$ YouTube videos available in March $2021$. However, by June $2021$, thirty videos had disappeared both from YouTube and the YouTube API for policy violation.

@@

Aside from the lack of data due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs. In particular, the $reach$ of posts on Facebook cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example). Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the APIs linked to Facebook, Twitter and YouTube. For the purposes of the present research we had to scrape this information (see section \ref{flags}). Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.

@@

{\bf Lack of transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.  The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}). For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}). Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube. To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content. More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets. For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended. Yet, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).

We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire. This is because, the prospective aimed users might find means to circumvent the partly automated interventions. To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}). Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks. To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}. For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds. In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link. For this case, we failed to understand precisely what kind of intervention the users were circumventing. Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.

@@

{\bf Scattered data.} Third, to study online misinformation, researchers, NGOs and data journalists turn to multiple APIs besides the official ones managed by the mainstream platforms themselves (e.g. BuzzSumo). They do so, because multiple data sources can be complementary and no specific API has complete data. {\color{red} [to be drafted by HT... and cite the article ~\cite{api} about APIs]....} we found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.

@@

%Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.

\subsection{Policy recommendations}

>>>>

In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: suspension of accounts, introduction of notices and flags and reducing the visibility of content. We have provided a methodology that can be useful for third-party monitoring. The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be useful to those working on addressing online misinformation. In the light of the present research, we discuss in this section data and policy related recommandations.

% For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.

%\subsection{Data related recommendations}

@@

{\bf Lack of data.} First, when Facebook, Twitter or YouTube intervene by suspending an account, a page or a channel, the data disappears. It can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research. This hampers the investigation of how platforms moderate content. To further illustrate this point, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$. We selected $94$ Facebook pages corresponding to our criteria. We then tried to collect the posts on these pages in January $2021$. But we discovered that $11$ pages could no longer be found and that the related data had disappeared from the CrowdTangle API. Similarly, when a YouTube channel gets suspended or a YouTube video is deleted the data related to them is removed from the YouTube API. For instance, the original list of YouTube videos from table \ref{tab2} with failed fact-checks, had over $200$ YouTube videos available in March $2021$. However, by June $2021$, thirty videos had disappeared both from YouTube and the YouTube API for policy violation.

@@

Aside from the lack of data due to suspensions, some essential metrics for the study of misinformation are not accessible via main APIs. In particular, the $reach$ of posts on Facebook {\color{red}(i.e. the number of people who actually see a given post)} cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example). Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs (with the only exceptions of two types of interstitials in Twitter API). For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube (see section \ref{flags}). Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact {\color{red} Misinformation review REF + others to show that we are not the only ones to say that}.

@@

{\bf Lack of transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.  The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}). {\color{red} For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}). Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.} To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content. More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets. For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended. Yet, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).

We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire. This is because, the prospective aimed users might find means to circumvent the partly automated interventions. {\color{red} To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}). Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks. To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}. For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds. In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link.} For this case, we failed to understand precisely what kind of intervention the users were circumventing. Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.

@@

{\bf Scattered data.} Third, to study online misinformation, researchers, NGOs and data journalists turn to multiple APIs besides the official ones managed by the mainstream platforms themselves (e.g. BuzzSumo). They do so, because multiple data sources can be complementary and no specific API has complete data. {\color{red} vs. scraping. [to be drafted by HT... and cite the article ~\cite{api} about APIs]...., article du NYTimes sur CT, APIs qui ouvrent et qui ferment, limites de l'API de Twitter entre la V1 et la V2.}

@@

{\bf Lack of coordination between platforms.}

{\bf Policies recommandations.}

\smallskip
%\subsection{Policy recommendations}
